Semantic Preserving Bijective Mappings for Expressions involving Special Functions between Computer Algebra Systems and Document Preparation Systems

### 2018-11-27 main.tex
Changes in the title: 'Representations of' to 'Expressions involving' (close #20)

\addbibresource{./bibliography/Bibliography.bib} 
\hypersetup{
	pdftitle	= {Semantic Preserving Bijective Mappings for Representations of Special Functions in Computer Algebra Systems and Document Preparation Systems}
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%% INFORMATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\title{
    Semantic Preserving Bijective Mappings for Representations of Special Functions between Computer Algebra Systems and Document Preparation Systems
}

>>>>

\addbibresource{./bibliography/Bibliography.bib} 
\hypersetup{
	pdftitle	= {Semantic Preserving Bijective Mappings for Expressions involving Special Functions in Computer Algebra Systems and Document Preparation Systems}
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%% INFORMATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\title{
    Semantic Preserving Bijective Mappings for Expressions involving Special Functions between Computer Algebra Systems and Document Preparation Systems
}
